\documentclass[10pt]{article}
\usepackage{charter}
% \usepackage{sourcecodepro-type1-autoinst}
% \usepackage{MinionPro}
\usepackage[usenames,dvipsnames,svgnames]{xcolor}
\usepackage{hyperref}
\usepackage[flushleft,neverdecrease,neveradjust]{paralist}
\usepackage{multicol}
\usepackage{tikz}
\usepackage{pifont}
\pagestyle{empty}
\usepackage{mdwlist}

\usepackage[left=.5cm,top=2cm,right=.5cm,bottom=1.5cm,nohead]{geometry}

%\usepackage[utf8]{inputenc}
%\pagenumbering{arabic}

\definecolor{darkgrey}{HTML}{333333}
\definecolor{grey}{HTML}{4D4D4D}
\definecolor{lightgrey}{HTML}{999999}
\definecolor{green}{HTML}{C2E15F}
\definecolor{orange}{HTML}{FDA333}
% \definecolor{purple}{HTML}{D3A4F9}
\definecolor{purple}{HTML}{9B59B6}
\definecolor{red}{HTML}{FB4485}
\definecolor{blue}{HTML}{6CE0F1}
\definecolor{zest}{HTML}{E67E22}
\linespread{1}
\renewcommand{\labelitemi}{}
\renewcommand{\labelitemii}{}

\newcommand{\lbar}[1]{{\color{#1}\ding{118}}\hspace*{2pt}}

\hypersetup{
  colorlinks=false,
  urlcolor=Sepia,
  %linkcolor=RoyalBlue,
  pdfborder= 0 0 0,
  bookmarks=false,
  pdftitle={Sidi Mohamed Beillahi - CV},
  pdfauthor={Sidi Mohamed Beillahi},
  pdfsubject={Curriculum Vitae},
  pdfkeywords={Sidi Mohamed Beillahi, resume, cv, mathematics, cs,
    computer science, phd, programming languages, concurrency, eventual
    consistency, parallelism, distributed systems,
    CAV, PLDI, CONCUR, FAC, weak consistency, relaxed memory, axiomatic semantics,
    operational semantics, solidity, smart contracts, asynchrony, synthesis, refinement,
}}

% http://tex.stackexchange.com/questions/110236/is-there-a-way-to-get-reverse-numbering-on-the-enumerate-environment
\newenvironment{benumerate}[2]{
    \let\oldItem\item
    \def\item{\addtocounter{enumi}{-2}\oldItem}
    \begin{enumerate}[#2] \itemsep3pt
    \setcounter{enumi}{#1}
    \addtocounter{enumi}{1}}
  {\end{enumerate}}

\newenvironment{education}[4]
{%\filbreak
\item
  \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2} \\
    #3 & \small{#4} \\
  \end{tabular*}
  % \begin{itemize} \setlength{\parskip}{-1pt}\item
  }
  { % \end{itemize}
}

\newcommand{\service}[1]{\item $\bullet$ \hspace{1ex}\parbox{7.2in}{#1}}

\newcommand{\positionnodesc}[2]
{%\filbreak
\item
  \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2}
  \end{tabular*}
}

\newenvironment{position}[4]
{%\filbreak
\item
  \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2} \\
    \hspace{1ex} #3 & \small{#4} \\
  \end{tabular*}
  % \begin{itemize} \setlength{\parskip}{-1pt}\item
  }
  { % \end{itemize}
}

\newenvironment{publication}[5]
{ \item
  \begin{tabular*}{7.5in}{p{6.3in}@{\extracolsep{\fill}}r}
    \href{#1}{\textbf{#2}} & \textit{#3}\\ #4 &\\ \textit{#5}&\\
  \end{tabular*}
} {}

\newenvironment{publicationCore}[6]
{ \item
  \begin{tabular*}{7.5in}{p{6.3in}@{\extracolsep{\fill}}r}
    \href{#1}{\textbf{#2}} & \textit{#3}\\ #4 & \textit{#5} \\ \textit{#6}&\\
  \end{tabular*}
} {}

\newenvironment{publicationNote}[6]
{ \item
  \begin{tabular*}{7.5in}{p{6.3in}@{\extracolsep{\fill}}r}
    \href{#1}{\textbf{#2}} & \textit{#3}\\ #4 &\\ \textit{#5}\\ \textbf{#6} \\
  \end{tabular*}
} {}

\newenvironment{talk}[4]
{ \item
  \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2} \\
    \hspace{1ex} #3 & \small{#4}
\end{tabular*}
} {}

\newcommand{\reference}[4]{%
  \begin{tabular}{@{}l@{}}%
    \textbf{#1}\\%
    #2\\%
    #3\\%
    \href{mailto:#4}{#4}%
  \end{tabular}%
}

\newcommand{\referencetwo}[5]{%
  \begin{tabular}{@{}l@{}}%
    \textbf{#1}\\%
    #2\\%
    #3\\%
    #4\\%
    \href{mailto:#5}{#5}%
  \end{tabular}%
}

\newcommand{\referencesmall}[6]{%
  \begin{tabular}{@{}l@{}}%
    \textbf{#1}\\%
    #2\\%
    #3\\%
    #4\\%
    #5\\%
    \href{mailto:#6}{#6}%
  \end{tabular}%
}


\newcommand{\refrow}[2]{%
\item \begin{tabular*}{0.9\textwidth}{@{}p{3.0in}@{\hspace*{0.3in}}p{3.0in}@{}} #1 & #2 \end{tabular*}
\vspace*{1ex}}

\newcommand{\refrowone}[1]{%
\item \begin{tabular*}{0.9\textwidth}{@{}p{3.0in}@{\hspace*{0.3in}}p{3.0in}@{}} #1 &  \end{tabular*}
\vspace*{1ex}} 

\newcommand{\refrowtwo}[2]{%
\item \begin{tabular*}{0.9\textwidth}{@{}p{3.0in}@{\hspace*{0.7in}}p{3.0in}@{}} #1 & #2 \end{tabular*}
\vspace*{1ex}}

\newenvironment{region}[3]{%
  \vspace*{0.5ex}
  {\scalebox{1.4}{\textbf{#1}}}
  \begin{benumerate}{#3}{\color{RoyalBlue}#2}}
  {\end{benumerate}\vspace{0.8ex}}

\newenvironment{nonumregion}[1]{%
\begin{region}{#1}{}{1}}
{\end{region}}

\newenvironment{itemregion}[1]{
  \vspace*{0.5ex}
  {\scalebox{1.4}{\textbf{#1}}}
  \begin{itemize}\itemsep1pt}
  {\end{itemize}\vspace{0.8ex}}

\newcommand{\oral}{{\color{PineGreen}\textsc{oral}}}
\newcommand{\poster}{{\color{BurntOrange}\textsc{poster}}}

\color{darkgrey}
\begin{document}

\begin{tikzpicture}[remember picture,overlay]
  \hypersetup{urlcolor=zest}
  \node [rectangle, fill=grey, anchor=north, minimum width=\paperwidth, minimum height=3.8cm] (box) at (current page.north){};
  \node [anchor=center] (name) at (box) {%
    \color{white}%
    \begin{tabular*}{7.5in}{@{\extracolsep{\fill}}lr}
      \\
      \textbf{\huge{Curriculum Vitae}} & \\*[2ex] %\today
      \textbf{\large{Sidi Mohamed Beillahi}} & {\url{https://beillahi.github.io}}\\[0.3ex]
      Postdoctoral Researcher & {\href{https://scholar.google.com/citations?user=qd4lM94AAAAJ}{Google Scholar}}\\[0.3ex]
      University of Toronto & {\href{https://www.linkedin.com/in/sidi-mohamed-beillahi}{Linkedin}}\\[0.3ex]
      %Toronto, Canada\\
      %\href{mailto:med.beillahi@gmail.com}{med.beillahi@gmail.com} & \emph{Tel}: \\
      \href{mailto:sm.beillahi@utoronto.ca}{sm.beillahi@utoronto.ca} & \\
      %\href{mailto:beillahi@irif.fr}{beillahi@irif.fr}
      %& \emph{Tel}: \textrm{+33 (0) 7 61 84 11 66}\\
    \end{tabular*}
  };
\end{tikzpicture}
\vspace{0.9in}

\hypersetup{urlcolor=cyan}

\begin{nonumregion}{\lbar{black}Research Interests}
\item \hspace{1ex} \parbox{7.3in}{Software verification; Software security; Distributed systems; Blockchain; Formal verification; Algorithmic verification; Programming languages; Program synthesis.}
\end{nonumregion}

\begin{nonumregion}{\lbar{black}Education}
  \begin{education}{Ph.D. --- Computer Science}
    {Dec 2017 -- Mar 2021}
    {}
    {Paris Diderot University, France}
    \vspace{-3ex}
    \item
      \begin{itemize}
      \item Thesis: \href{https://beillahi.github.io/papers/thesis.pdf}{\textbf{Automated Verification of Programs Running on top of Distributed Systems}}
        \vspace{-0.5ex}
      \item Advisors: Ahmed Bouajjani and Constantin Enea
      \end{itemize}
  \end{education}
  \begin{education} {Master of Applied Science --- Computer Engineering}
    {Sep 2014 -- Nov 2016}
    {}
    {Concordia University, Canada}
    \vspace{-3ex}
    \item
      \begin{itemize}
      \item Thesis: \href{https://beillahi.github.io/papers/MasterThesis.pdf}{\textbf{Towards the Design Automation of Quantum Circuits}}
        \vspace{-0.5ex}
      \item Advisor: Sofi\`{e}ne Tahar
      \end{itemize}
  \end{education}
  \begin{education} {Engineer's Degree --- Polytechnicien}
    {Sep 2011 -- Jun 2014}
    {}
    {Tunisia Polytechnic School, Tunisia} %University of Carthage
    \vspace{-3ex}
    \item
      \begin{itemize}
      \item Thesis Title: \href{https://beillahi.github.io/}{\textbf{Formalization of Signal-Flow Graphs in HOL}}
        \vspace{-0.5ex}
      \item Advisor: Sofi\`{e}ne Tahar
      \end{itemize}
  \end{education}

  \item
  \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{DEUPC --- Mathematics and Physics} & \textit{Sep 2009 -- Jun 2011} \\
     & \small{Sfax Preparatory Engineering Institute} \\
    & \small{University of Sfax, Tunisia}
  \end{tabular*}
  \vspace{-12pt}

\end{nonumregion}

\begin{nonumregion} {\lbar{black}Experience}
	%\positionnodesc{Assistant Professor, Indian Institute of Technology, Madras}{Jan 2019 -- present}
  %\begin{position}{Senior Research Associate, University of Cambridge}{Nov 2017 -- Dec 2018}{Advisors: Alan Mycroft, Anil Madhavapeddy}{Cambridge, UK}
  %\end{position}
  %\begin{position}{Chief Technology Officer, OCaml Labs Consultancy Ltd.}{Aug 2016 -- present}{}{Cambridge, UK}
  %  {Focussed on building the OCaml Platform: infrastructure to build, test, document and deploy OCaml-based software.}
  %\end{position}
  \begin{position}{NSERC Postdoctoral Research Fellow, University of Toronto}{Jun 2021 -- present}
		{Advisors: Fan Long and Andreas Veneris}{Toronto, Canada}
    %\hspace{-3cm}{ Postdoctoral Research Fellow since January 2023}
  \end{position}
  %\positionnodesc{ Postdoctoral , University of Toronto}{Jan 2023 -- present}
  \positionnodesc{Mitacs Accelerate Postdoctoral Fellow, University of Toronto and Bank of Canada}{Sep 2022 -- present}
		%{Advisors: Fan Long and Andreas Veneris}{Toronto, Canada}
  %\end{position}
  \positionnodesc{Research Consultant, Conflux Network}{Dec 2021 -- present}
  \positionnodesc{Course Instructor, University of Toronto}{Sep 2022 -- Apr 2023}
  \begin{position}{Research Assistant, Institut de Recherche en Informatique Fondamentale}{Dec 2017 -- May 2021}
		{Advisors: Ahmed Bouajjani and Constantin Enea}{Paris, France}
  \end{position}
  \positionnodesc{Teaching Assistant, Paris Diderot University}{Sep 2018 -- Jan 2021}
  \begin{position}{Research Intern, SRI International}{Apr 2019 -- Aug 2019}
		{Advisor: Michael Emmi}{New York City, USA}
  \end{position}
  \begin{position}{Software Programmer, TRU Simulation + Training}{May 2017 -- Dec 2017}
      {}{Montr\'{e}al, Canada}
  \end{position}
  \begin{position}{Research Assistant, Concordia University}{Mar 2014 -- Nov 2016}
		{Advisor: Sofi\`{e}ne Tahar}{Montr\'{e}al, Canada}
  \end{position}
  \positionnodesc{Teaching Assistant, Concordia University}{Sep 2015 -- May 2016}
  \begin{position}{Research Engineer, Marinvent inc.}{Mar 2016 -- Nov 2016}
		{Advisor: Sofi\`{e}ne Tahar}{Montr\'{e}al, Canada}
  \end{position}
  
  \begin{position}{Intern, STMicroelectronics}{Jul 2013 -- Aug 2013}
    {Advisor: Mohamed Ben Ahmed}{Tunis, Tunisia}
  \end{position}

  
  \begin{position}{Intern, Mauritel S.A}{Aug 2012 -- Aug 2012}
    {Advisor: Mohamed Moujtaba}{Nouakchott, Mauritania}
  \end{position}

  %\item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
  %  \textbf{Teaching Assistant, Purdue University} & \small{West Lafayette, IN, USA}\\
  %  \hspace{1ex} Undergraduate C Programming (CS180) & \textit{Aug 2012 -- Dec 2012} \\
  %  \hspace{1ex} Graduate Programming Languages (CS565) & \textit{Aug 2011 -- Dec 2011} \\
  %  \end{tabular*}

\end{nonumregion}

%\begin{nonumregion}{\lbar{Mahogany}Software Programming Skills}
%  \item \hspace{1ex} \parbox{7.3in}{C\#, C/C++, Python, Ocaml, Solidity, Typescript, Boogie, HOL Light, Civl verifier, System Verilog, VHDL, assembly language (Intel, PIC, Cortex M, and EVM), Latex.}
%\end{nonumregion}

\begin{itemregion} {\lbar{black}Awards and Recognitions}
  \service{Invited to a Journal Special Issue for Selected OSDI 2023 papers, 2023.}
  \service{IEEE ICBC Distinguished Paper Award, 2022.}
  \service{Invited to a Journal Special Issue for Selected CONCUR 2019 Papers, 2019.}
  \service{Best Undergraduate Thesis, Tunisia Polytechnic School, 2014.}
  \service{Ranked 31st in the National Grandes Ecoles Exam, Tunisia, 2011.}
  \service{Olympian in the International Mathematical Olympiad, Germany, 2009.}
  \service{Ranked 3rd in the National Mathematical Olympiad, Mauritania, 2009.}
  \service{Ranked 1st in the National Bac Exam in Mathematics, Mauritania, 2009.}
\end{itemregion}

\begin{itemregion} {\lbar{black}Grants and Scholarships}
  \service{NSERC Postdoctoral Fellowship, 2022 -- 2024, CAD 90,000.}
  \service{Smart Contract Research Forum Grant, 2022, USD 1,000.}
  \service{VMW Scholarship Award for CAV 2016, USD 650.}
  \service{Concordia Graduate Student Association Conference Funding for CAV 2016, CAD 100.}
  \service{Concordia University Conference and Exposition Award for NFM 2016, CAD 1,000.}
  \service{Graduate Student Support Program, Concordia University, 2014 -- 2016, CAD 20,000.}
  \service{National Scholarship, Mauritania, 2009 -- 2014, EUR 13,500.}
  \service{Scholarship Award to Participate in the International Mathematical Olympiad, Mauritania, 2009, EUR 1,000.}
\end{itemregion}

\begin{itemregion} {\lbar{black}Service}
  \service{Co-organizer, Institut de Recherche en Informatique Fondamentale Verification Seminar, Mar 2020 -- July 2020.}
  \service{Artificat Evaluation Committees: POPL 2021-2022, CAV 2021, OOPSLA 2021-2022.}
  \service{Extended Review Committees: OOPSLA 2022.}
  \service{Sub-Reviewer: FTSCS 2016, VMCAI 2020, CAV 2020, Blockchain 2021, ICDCS 2022, ICBC 2022-2023, TACAS 2024.}
  \service{Journal Invited Reviewer:  IEEE Transactions on Network and Service Management}
  \service{Student Volunteer: CAV 2016.}
	%\service{Organizer, }
	%\service{Editor,}
	%\service{Program Committee Chair: }
  %\service{Program Committee member: }
	%\service{External Review Committee: }
  %\service{Artifact Evaluation Committee member: } \vspace{0.5ex}
	%\service{Interviewer }
\end{itemregion}

%\begin{region} {\lbar{purple}Edited Publications}{{E}1}{1}
%
%\end{region}

\begin{region} {\lbar{black}Journal Publications}{{J}1}{5}

  \begin{publicationNote} {https://beillahi.github.io}
		{LVMT: An Efficient Authenticated Storage for Blockchain} 
		{2023} {Chenxing Li, \textbf{Sidi Mohamed Beillahi}, Guang Yang, Ming Wu, Wei Xu, Fan Long}
		{Under submission to the ACM Transactions on Storage}
    {Invited special issue for best storage papers from OSDI 2023}
  \end{publicationNote}

  \begin{publicationNote}{https://arxiv.org/pdf/LMPTExt.pdf}
    {LMPT: A Novel Authenticated Data Structure to Eliminate Storage Bottlenecks for High Performance Blockchains}
    {2023}{Jemin Andrew Choi, \textbf{Sidi Mohamed Beillahi}, Srisht Fateh Singh, Panagiotis Michalopoulos, Peilun Li, Andreas Veneris, Fan Long}
    {Accepted to the IEEE Transactions on Network and Service Management}
    {Invited special issue for best papers from ICBC 2022}
  \end{publicationNote}

  \begin{publication} {https://beillahi.github.io/papers/OOPSLA22.pdf}
		{SigVM: Enabling Event-Driven Execution for Truly Decentralized Smart Contracts}
		{Oct 2022} {Zihan Zhao, \textbf{Sidi Mohamed Beillahi}, Ryan Song, Yuxi Cai, Andreas Veneris, Fan Long}
		{Proceedings of the ACM on Programming Languages, 6(OOPSLA2), 149:673 -- 149:698}
  \end{publication}

  \begin{publicationNote}{https://arxiv.org/pdf/1906.12095v5.pdf}
    {Robustness Against Transactional Causal Consistency}
    {Feb 2021}{\textbf{Sidi Mohamed Beillahi}, Ahmed Bouajjani, Constantin Enea}
    {Logical Methods in Computer Science, 17(1): 12:1 -- 12:42}
    {Invited special issue for selected papers from CONCUR 2019}
  \end{publicationNote}


  \begin{publication}{https://beillahi.github.io/papers/FAC19.pdf}
    {A Modeling and Verification Framework for Optical Quantum Circuit}
    {Mar 2019}{\textbf{Sidi Mohamed Beillahi}, Mohamed Yousri Mahmoud, Sofi\`{e}ne Tahar}
    {Formal Aspects of Computing, 31(3): 321 -- 351}
  \end{publication}
\end{region}
%\newpage
\begin{region} {\lbar{black}Conference Publications}{{C}1}{17}

  \begin{publication} {https://beillahi.github.io}
		{Dymisfying Invariant Effectiveness for Securing Smart Contracts} 
		{2023} {Zhiyang Chen, Ye Liu, \textbf{Sidi Mohamed Beillahi}, Yi Li, Fan Long}
		{under submission}
  \end{publication}
 
  \begin{publication} {https://arxiv.org/pdf/2206.10708.pdf}
		{FlashSyn: Flash Loan Attack Synthesis via Counterexample-Driven Approximation} 
		{2024} {Zhiyang Chen, \textbf{Sidi Mohamed Beillahi}, Fan Long}
		{Accepted to the 46th International Conference on Software Engineering (ICSE 2024)}
  \end{publication}

  \begin{publication} {https://beillahi.github.io}
		{Safeguarding DeFi Smart Contracts against Oracle Deviations} 
		{2024} {Xun Deng, \textbf{Sidi Mohamed Beillahi}, Cyrus Minwalla, Han Du, Andreas Veneris, Fan Long}
		{Accepted to the 46th International Conference on Software Engineering (ICSE 2024)}
  \end{publication}



  \begin{publication} {https://beillahi.github.io/papers/OSDI23.pdf}
		{LVMT: An Efficient Authenticated Storage for Blockchain} 
		{July 2023} {Chenxing Li, \textbf{Sidi Mohamed Beillahi}, Guang Yang, Ming Wu, Wei Xu, Fan Long}
		{In Proc. 17th USENIX Symposium on Operating Systems Design and Implementation (OSDI), 2023}
    {\\ \textbf{Invited to a Special Issue of the ACM Transactions on Storage Journal for Selected OSDI 2023 Papers.}}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/DAPPS23.pdf}
		{A Robust Front-Running Methodology for Malicious Flash-Loan DeFi Attacks} 
		{July 2023} {Xun Deng, Zihan Zhao, \textbf{Sidi Mohamed Beillahi}, Han Du, Cyrus Minwalla, Keerthi Nelaturu, 
    Andreas Veneris, Fan Long}
		{In Proc. IEEE International Conference on Decentralized Applications and Infrastructures (DAPPS), 2023}
  \end{publication}
 
  \begin{publication} {https://beillahi.github.io/papers/ICBC23.pdf}
		{Möbius: an Atomic State Sharding Design for Account-Based Blockchains} 
		{May 2023} {Srisht Fateh Singh, Panagiotis Michalopoulos, \textbf{Sidi Mohamed Beillahi}, Andreas Veneris, Fan Long}
		{In Proc. IEEE International Conference on Blockchain and Cryptocurrency (ICBC), 2023}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/NETYS23.pdf}
		{Comparing Causal Convergence Consistency Models}
		{May 2023} {\textbf{Sidi Mohamed Beillahi}, Ahmed Bouajjani, Constantin Enea}
		{In Proc. 11th International Conference on Networked Systems (NETYS), 2023}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/SAS22.pdf}
		{Automated Synthesis of Asynchronizations}
		{Dec 2022} {\textbf{Sidi Mohamed Beillahi}, Ahmed Bouajjani, Constantin Enea, Shuvendu Lahiri}
		{In Proc. 29th Static Analysis Symposium (SAS), 2022}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/2022040426.pdf}
		{Automated Auditing of Price Gouging TOD Vulnerabilities in Smart Contracts}
		{May 2022} {\textbf{Sidi Mohamed Beillahi}, Eric Keilty, Keerthi Nelaturu, Andreas Veneris, Fan Long}
		{In Proc. IEEE International Conference on Blockchain and Cryptocurrency (ICBC), 2022}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/2022044041.pdf}
		{LMPTs: Eliminating Storage Bottlenecks for Processing Blockchain Transactions}
		{May 2022} {Jemin Andrew Choi, \textbf{Sidi Mohamed Beillahi}, Peilun Li, Andreas Veneris, Fan Long}
		{In Proc. IEEE International Conference on Blockchain and Cryptocurrency (ICBC), 2022}
    {\\ \textbf{IEEE ICBC Distinguished Paper Award.}}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/BRAINS21.pdf}
		{Smart Contracts Refinement for Gas Optimization}
		{Sep 2021} {Keerthi Nelaturu, \textbf{Sidi Mohamed Beillahi}, Fan Long, Andreas Veneris}
		{In Proc. 3rd Conference on Blockchain Research \& Applications for Innovative Networks and Services (BRAINS), 2021}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/ESOP21.pdf}
		{Checking Robustness Between Weak Transactional Consistency Models}
		{Mar 2021} {\textbf{Sidi Mohamed Beillahi}, Ahmed Bouajjani, Constantin Enea} 
		{In Proc. 30th European Symposium on Programming (ESOP), 2021} 
  \end{publication}

	\begin{publication} {https://beillahi.github.io/papers/PLDI20.pdf}
		{Behavioral Simulation for Smart Contracts}
		{Jun 2020} {\textbf{Sidi Mohamed Beillahi}, Gabriela Ciocarlie, Michael Emmi, Constantin Enea}
		{In Proc. 41st annual ACM SIGPLAN conference on Programming Language Design and Implementation (PLDI), 2020}
  \end{publication}

	\begin{publication} {https://beillahi.github.io/papers/CONCUR19.pdf}
		{Robustness Against Transactional Causal Consistency}
		{Sep 2019} {\textbf{Sidi Mohamed Beillahi}, Ahmed Bouajjani, Constantin Enea}
    {In Proc. 30th International Conference on Concurrency Theory (CONCUR), 2019}
    {\\ \textbf{Invited to a Special Issue of the Logical Methods in Computer Science Journal for Selected CONCUR 2019 Papers.}}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/CAV19.pdf}
    {Checking Robustness Against Snapshot Isolation}
    {Jul 2019} {\textbf{Sidi Mohamed Beillahi}, Ahmed Bouajjani, Constantin Enea}
    {In Proc. 31st International Conference on Computer Aided Verification (CAV), 2019}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/NFM16.pdf}
    {Hierarchical Verification of Quantum Circuits}
    {Jun 2016} {\textbf{Sidi Mohamed Beillahi}, Mohamed Yousri Mahmoud, Sofi\`{e}ne Tahar}
    {In Proc. 8th International Symposium NASA Formal Methods (NFM), 2016}
  \end{publication}

  \begin{publication} {https://beillahi.github.io/papers/ICFEM15.pdf}
    {Formal Analysis of Power Electronic Systems}
    {Nov 2015} {\textbf{Sidi Mohamed Beillahi}, Umair Siddique, Sofi\`{e}ne Tahar}
    {In Proc. 17th International Conference on Formal Engineering Methods (ICFEM), 2015}
  \end{publication}

\end{region}

%\newpage
\begin{region} {\lbar{black}Workshop Publications}{{W}1}{3}

	\begin{publication}{https://beillahi.github.io/papers/NSV16.pdf}
		{Formal Analysis of Engineering Systems Based on Signal-Flow-Graph Theory}
		{Jul 2016}{\textbf{Sidi Mohamed Beillahi}, Umair Siddique, Sofi\`{e}ne Tahar}
		{In Proc. 9th International Workshop Numerical Software Verification (NSV-CAV), 2016}
  \end{publication}

	\begin{publication}{https://beillahi.github.io/papers/FMICS15.pdf}
		{On the Formal Analysis of Photonic Signal Processing Systems}
		{Jun 2015}{Umair Siddique, \textbf{Sidi Mohamed Beillahi}, Sofi\`{e}ne Tahar}
    {In Proc. 20th International Workshop Formal Methods for Industrial Critical Systems (FMICS), 2015}
  \end{publication}
  
  \begin{publication}{https://beillahi.github.io/papers/ARW15.pdf}
		{A Tool for the Formal Verification of Quantum Optical Computing Systems}
		{Apr 2015}{\textbf{Sidi Mohamed Beillahi}, Mohamed Yousri Mahmoud, Sofi\`{e}ne Tahar}
    {In Proc. Automated Reasoning Workshop (ARW), 2015}
  \end{publication}
  
\end{region}
%\newpage
%\begin{region} {\lbar{purple}Technical Reports and Drafts}{{T}1}{1}
%
%  \begin{publication}{https://beillahi.github.io}
%    {}
%    {Nov 2014}{}
%    {Concordia University Computer Engineering Technical Report -- TR-11-018}
%  \end{publication}
%
%\end{region}

%\begin{itemregion}{\lbar{red}Teaching/Advising}
\begin{itemregion}{\lbar{black}Teaching}
  %\service{Lecturer:}
  %\service{Guest Lectures:}
  %\service{Supervisions at Concordia University:}
  \service{Course Co-Instructor at University of Toronto}
  \begin{itemize}
    \service{CSC323H1S: Principles of Programming Languages for 3rd Year Computer Science Students, Jan 2023 -- Apr 2023.}
    \service{ECE345H1F: Algorithms \& Data Structures for 3rd Year Computer Engineering Students, Sep 2022 -- Dec 2022.}
  \end{itemize}

  \service{Teaching Assistantships at Paris Diderot University}
  \begin{itemize}
    \service{Automata and Lexical Analysis for 2nd Year Computer Science Students, Sep 2020 -- Dec 2020.}
    \service{Principles of Binary Machines for 1st Year Computer Science Students, Sep 2020 -- Dec 2020.}
    \service{Java Programming for 1st Year Computer Science Students, Sep 2019 -- Dec 2019.}
    \service{Principles of Object-Oriented Programming in Java for 2nd Year Computer Science Students, Sep 2019 -- Dec 2019.}
    \service{Python Programming for 1st Year Social Science Students, Sep 2018 -- Dec 2018.}
    \service{Relational Databases and SQL for 2nd Year Computer Science Students, Sep 2018 -- Dec 2018.}
  \end{itemize}
  \service{Teaching Assistantships at Concordia University}
  \begin{itemize}
    \service{Hardward Functional Verification for Graduate and Senior Undergraduate Students, Jan 2016 -- Apr 2016.}
    \service{Computer Architecture and Design for Graduate Students, Jan 2016 -- Apr 2016.}
    \service{Digital Design for Undergraduate Students, Jan 2016 -- Apr 2016.}
    \service{Microprocessors and their Applications for Graduate Students, Sep 2015 -- Dec 2015.}
  \end{itemize}
  %\service{Projects supervised:}
\end{itemregion} 


\begin{nonumregion}{\lbar{black}Professional Affiliations}
  \item \hspace{1ex} \parbox{7.3in}{ACM (2020); IEEE (2022).}
\end{nonumregion}

\newpage

\begin{itemregion}{\lbar{black}Supervision}
  %\service{Lecturer:}
  %\service{Guest Lectures:}
  %\service{Supervisions at Concordia University:}
  \service{Keerthi Nelaturu, Ph.D. student, University of Toronto}
  \service{Zihan Zhao, MASc student, University of Toronto - graduated in 2022}
  \service{Zhiyang Chen, Ph.D. student, University of Toronto}
  \service{Eric Keilty, MASc student, University of Toronto - graduated in 2023}
  \service{Srisht Fateh Singh, MASc student, University of Toronto - graduated in 2023}
  \service{Hossein Ghotbaddini, MASc student, University of Toronto - graduated in 2023}
  \service{Xun Deng, MASc student, University of Toronto}
  \service{Vladyslav Nekriach, MASc student, University of Toronto}
  \service{Jacky Zhou, MASc student, University of Toronto}
  %\service{Projects supervised:}
\end{itemregion} 

%\newpage
\begin{itemregion}{\lbar{black}Talks}


  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Automated Synthesis of Asynchronizations} \\
    \hspace{1ex} SAS 2022 at SPLASH 2022, Auckland, New Zealand  & \textit{Dec 2022}
  \end{tabular*}

  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{SigVM: Enabling Event-Driven Execution for Truly Decentralized Smart Contracts} \\
    \hspace{1ex} OOPSLA 2022 at SPLASH 2022, Auckland, New Zealand  & \textit{Dec 2022}\\
    \hspace{1ex} Research Meeting with Bank of Canada, University of Toronto  & \textit{Jul 2022}
  \end{tabular*}

  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Automated Auditing of Price Gouging TOD Vulnerabilities in Smart Contracts} \\
    \hspace{1ex} ICBC 2022, Shanghai, China (virtual)  & \textit{May 2022}
  \end{tabular*}

  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Checking Robustness Between Weak Transactional Consistency Models} \\
    \hspace{1ex} ANR Project AdeCoDS Meeting, LIP6, Sorbonne University (virtual)  & \textit{Jun 2021} \\
    \hspace{1ex} IRIF Verification Seminar, Paris Diderot University (virtual)  & \textit{May 2021} \\
    \hspace{1ex} ESOP 2021, Luxembourg, Luxembourg (virtual)  & \textit{Mar 2021}
  \end{tabular*}

  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \textbf{Behavioral Simulation for Smart Contracts} \\
    \hspace{1ex} COVID papers at SPLASH 2022, Auckland, New Zealand & \textit{Dec 2022} \\
    \hspace{1ex} GROUP SEMINAR, University of Toronto (virtual) & \textit{Dec 2021} \\
    \hspace{1ex} SEMINAR UM6P-CS, Morocco (virtual) & \textit{Jul 2020} \\
    \hspace{1ex} PLDI 2020, London, UK (virtual)  & \textit{Jun 2020}
  \end{tabular*}

  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
          \textbf{Robustness Against Transactional Causal Consistency} \\
          \hspace{1ex} IRIF Verification Seminar, Paris Diderot University    & \textit{Dec 2019} \\
          \hspace{1ex} CONCUR 2019, Amsterdam, Netherlands  & \textit{Sep 2019}
        \end{tabular*}

  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
        \textbf{Checking Robustness Against Snapshot Isolation} \\
        \hspace{1ex} ANR Project AdeCoDS Kick-off Meeting, IRIF, Paris Diderot University  & \textit{Nov 2019} \\
        \hspace{1ex} CAV 2019, New York City, USA  & \textit{Jul 2019}
      \end{tabular*}

  \begin{talk}{Formal Analysis of Engineering Systems Based on Signal-Flow-Graph Theory}
    {Jul 2016}{NSV-CAV 2016}{Toronto, Canada}
  \end{talk}

  \begin{talk}{Hierarchical Verification of Quantum Circuits}
    {Jun 2016}{NFM 2016}{Minneapolis, USA}
  \end{talk}

  \begin{talk}{Formal Analysis of Power Electronic Systems}
    {Oct 2015}{Hardware Verification Group Meeting}{Concordia University}
  \end{talk}

  \begin{talk}{On the Formal Analysis of Photonic Signal Processing Systems}
    {May 2015}{Hardware Verification Group Meeting}{Concordia University}
  \end{talk}
\end{itemregion}
\begin{itemregion}{\lbar{black}Recent media articles on the work published in C17}
  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
   \href{https://www.coindesk.com/tech/2023/08/23/blockchain-security-firm-quantstamp-hopes-to-battle-flash-loan-attacks-with-new-service/}{Blockchain Security Firm Quantstamp Hopes to Battle Flash Loan Attacks With New Service} & \textit{CoinDesk - Aug 2023}
  \end{tabular*}
  
  \item \begin{tabular*}{7.5in}{l@{\extracolsep{\fill}}r}
    \href{https://www.theblock.co/post/246956/quantstamp-tool-to-thwart-defi-flash-loan-attacks}{Quantstamp unveils tool to detect DeFi flash loan vulnerabilities} & \textit{THE BLOCK - Aug 2023}
   \end{tabular*}
  \end{itemregion} 

%\newpage
\ifdefined\genrefs

\begin{nonumregion}{\lbar{black}Contacts of Three Reference Letter Writers}
  \refrowtwo{
    \referencetwo{Ahmed Bouajjani}
    {Professor}
    {Paris Diderot University}
    {Senior member of the Institut Universitaire de France}
    {abou@irif.fr}
  }{
    \reference{Andreas Veneris}
    {Professor and Connaught Scholar}
    {University of Toronto}
    {veneris@eecg.toronto.edu}
  }
  \refrowone{
    \reference{Fan Long}
    {Assistant Professor}
    {University of Toronto}
    {fanl@cs.toronto.edu}
  }
\end{nonumregion}

\fi

\end{document}


%  LocalWords:  Burchill
%  LocalWords:  Uncertainity 
%  LocalWords:  Corso Fellbaum 
%  LocalWords:  Colloquia 
